Regular singular Volterra equations on complex domains

### 2023-08-29 reg-sing-volterra.tex
Work on replacing cond:slow with revised cond:diag-basic

% list formatting
\newlist{conditions}{itemize}{1}
\setlist[conditions]{leftmargin=24mm, rightmargin=12mm}
\makeatletter
% hat tip TeX.SE user31729
%   https://tex.stackexchange.com/a/328393/6934
\newcommand{\cond}[1]{\item[(\textsc{#1})]\protected@edef\@currentlabel{\textsc{#1}}}
\newcommand{\condconst}[2]{\item[($\text{\textsc{#1}} \mid #2$)]\protected@edef\@currentlabel{$\text{\textsc{#1}} \mid #2$}}
\makeatother

@@

\item Show that example satisfies Condition~\eqref{cond:sing}.

@@

  \item Add $c_\Delta$ to Condition~\eqref{cond:diag-basic} as multiplicative constant, and export both of the constants $\lambda_\Delta$ and $\lambda_0 = \lambda_\Delta + c_\Delta$ from the condition.
  \item When showing that the example satisfies Condition~\eqref{cond:diag-basic}, make it consistent with new condition wording.

@@

Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain. In Section~\ref{sec:example}, we'll see this helpful behavior in the class of differential equations that Ecalle calls {\em level~1}, which includes classical examples like the modified Bessel equation, the equations describing the vibration modes of beams that taper in certain ways \textcolor{orange}{[find citation]}, and the Airy equation after a change of coordinate. This last example generalizes to some level 1 equations that feature in current research, like the Airy-Lucas and higher Airy equations~\cite[Equations 3.2 and 3.8]{charbonnier22}\cite{durugo_higher}.

@@

Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}. We'll achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}. We'll apply our results to level $1$ differential equations in Section~\ref{sec:example}.
\subsection{Notation for uniform bounds}
Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we'll write $\varphi \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$. Unless we say otherwise, the bound holds throughout the domain where both functions are defined.
\subsection{Setting}\label{setting}
\subsubsection{The domain}\label{setting:domain}
Throughout this paper, as described in Section~\ref{motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$. We also assume:
\begin{conditions}
\cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$. In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$. Since $\domain$ doesn't contain $\zeta = 0$, we'll always leave that starting point out of the path.
\end{conditions}
For the applications we have in mind, $\domain$ might look something like the set pictured below, which satisfies Condition~\eqref{cond:star}.
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
%% previously violet!20
\fill[ietcoast!33, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
%% previously violet
\fill[ietcoast!33!black] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
\end{tikzpicture}
\end{center}
\subsubsection{The prototype operator}\label{setting:basic}
The prototypical example of the kind of operator we'll be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.

Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
\[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:
\begin{conditions}
\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---the {\em residue} of the singularity---the difference
\[ \hardker(a, a) - \frac{\tau}{\zeta(a)} \]
is bounded on a neighborhood of $\zeta(a) = 0$ in $\domain$.

In addition, for each $\sigma > \tau$, the bound
\[ |\hardker(a, a')| < \frac{\sigma}{\zeta(a)} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
\end{conditions}
We'll assume that $\tau$ is real and positive.

Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
\begin{verify}
[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded. By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition. Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
\end{verify}
For some of our results, we'll also need to control $|p|$ and $|q|$ in various ways as $|\zeta|$ goes to infinity.
\begin{conditions}
\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
\begin{align*}
\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
\end{align*}
outside some neighborhood of $\zeta = 0$ in $\domain$. In addition, $|1/p|$ and $|q/p|$ are bounded outside every neighborhood of $\zeta = 0$ in $\domain$; the bound may depend on the neighborhood. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point. The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
\end{conditions}
This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
\begin{conditions}
\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} We can find a constant $\lambda_\Delta$ with
\[ \big| \hardker(a, a') \big| \lesssim e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
over all $a$ in $\domain$ outside some neighborhood of $\zeta = 0$, and all $a' \in \domain$.
%%outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
\end{conditions}
We'll occasionally mention an optional condition on $p$ that allows us to state our main results more explicitly.
\begin{conditions}
\condconst{reg-p}{B, \epsilon}\label{cond:reg-p}
For some non-zero constant $B$ and some $\epsilon > 0$,
\[ p \in B\zeta + O\big(|\zeta|^{1 + \epsilon}\big) \]
at $\zeta = 0$.
\end{conditions}
\subsubsection{The perturbed operator}\label{setting:perturbed}

Now, let's perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$. The perturbation $\softpart$ doesn't have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we'll show in Proposition \ref{prop:smoothing}). To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\Omega^2$. This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.

@@

Now, using Condition~\eqref{cond:sing} again, choose some $\sigma > \tau$ and find a radius $r < \delta$ for which
\[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we can deduce that
\begin{align*}
|\solproto| & \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p}\right|\,|\zeta|^\tau \\
& \lesssim \left|\frac{1}{q(b')}\right|\,\frac{\sigma}{|\zeta|}\,|\zeta|^\tau \\
& \lesssim |\zeta|^{\tau-1}
\end{align*}
on the region $|\zeta| < r$, as desired.
\end{proof}
\begin{prop}\label{prop:asymptotic at infinity}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \textcolor{brown}{\eqref{cond:diag-basic}} \textcolor{MediumSpringGreen}{\eqref{cond:slow}}. Then $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
\end{prop}
\begin{proof}
We want to show that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$.

@@

\color{Brown}By removing a bounded neighborhood of $\zeta = 0$ from $\domain$, make a set $\domain_\text{far}$ with
\[ \hardker(a, a') \le c_\Delta e^{\lambda_\Delta |\zeta(a) - \zeta(a')|}, \]
for all $a \in \domain_\text{far}$ and $a' \in \domain$, as Condition~\eqref{cond:diag-basic} says we can do. Applying this bound on the diagonal in $\domain_\text{far}^2$, we learn that $|q/p| \le c_\Delta$ on $\domain_\text{far}$. In addition, by fixing some arbitrary  $b' \in \domain$, see that
\begin{align*}
\left|\frac{q(b')}{p(a)}\right| & \lesssim e^{\lambda_\Delta|\zeta(a) - \zeta(b')|} \\
& \lesssim e^{\lambda_\Delta(|\zeta(a)| + |\zeta(b')|)} \\
& \lesssim e^{\lambda_\Delta|\zeta(a)|} e^{\lambda_\Delta|\zeta(b')|} \\
& \lesssim e^{\lambda_\Delta|\zeta(a)|}
\end{align*}
over all $a \in \domain_\text{far}$. Hence, $|1/p| \lesssim e^{\lambda_\Delta|\zeta|}$ on $\domain_\text{far}$. Using both of the bounds we just found, we reason that
\begin{align*}
|\solproto(a)| & = \left| \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \right| \\
& \le \left|\frac{1}{p(a)}\right| \exp\left(\int_{b}^{a}\left|\frac{q}{p}\right|\;d\zeta\right) \\
& \lesssim e^{\lambda_\Delta|\zeta(a)|}\,e^{c_\Delta(|\zeta(a)| + |\zeta(b)|)} \\
& \lesssim e^{(\lambda_\Delta + c_\Delta)|\zeta(a)|}\,e^{c_\Delta|\zeta(b)|} \\
& \lesssim e^{\lambda_0|\zeta(a)|}
\end{align*}
over all $a \in \domain_\text{far}$, recalling that $\lambda_0 = \lambda_\Delta + c_\Delta$. Since $\domain_\text{far}$ avoids a neighborhood of $\zeta = 0$, we know $|\zeta|^{\tau-1}$ is bounded on $\domain_\text{far}$. Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{far}$.
\color{black}

\color{MediumSpringGreen}
Recall that in Condition~\eqref{cond:slow}, the constant $\lambda_0$ is the sum of two constants: $\lambda_p$, which controls the growth of $1/p$ at infinity, and $\lambda_\text{ratio}$, which controls the growth of $p/q$ at infinity. By removing a bounded neighborhood of $\zeta = 0$ from $\domain$, make a set $\domain_\text{far}$ where $|1/p| \lesssim e^{\lambda_p |\zeta|}$ and $|q/p| \le \lambda_\text{ratio}$, as Condition~\eqref{cond:slow} says we can do. Observe that
\begin{align*}
|\solproto(a)| & = \left| \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \right| \\
& \le \left|\frac{1}{p(a)}\right| \exp\left(\int_{b}^{a}\left|\frac{q}{p}\right|\;d\zeta\right) \\
& \lesssim e^{\lambda_p|\zeta(a)|}\,e^{\lambda_\text{ratio}(|\zeta(a)| + |\zeta(b)|)} \\
& \lesssim e^{\lambda_0|\zeta(a)|}\,e^{\lambda_\text{ratio}|\zeta(b)|} \\
& \lesssim e^{\lambda_0|\zeta(a)|}
\end{align*}
over all $a \in \domain_\text{far}$. Since $\domain_\text{far}$ avoids a neighborhood of $\zeta = 0$, we know $|\zeta|^{\tau-1}$ is bounded on $\domain_\text{far}$. Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{far}$.
\color{black}

Finally, let $\domain_\text{mid}$ be the set that remains when you remove $\domain_\text{near}$ and $\domain_\text{far}$ from $\domain$. Since $\domain_\text{mid}$ avoids $\zeta = 0$ and is bounded, $|\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ can't get arbitrarily small there, and \textcolor{MediumSpringGreen}{Condition~\eqref{cond:slow} [add a new condition for this]} guarantees that $|\solproto|$ is bounded there. Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{mid}$.

@@

For the kernel $\hardker$ the claim follows from Condition \eqref{cond:sing}, namely for any $\sigma>\tau$ we can find a neighbourhood of $(0,0)\in\domain^2$ such that 
\[ |\hardker(a, a')| \le \frac{\sigma}{|\zeta(a)|}. \]
\color{RoyalBlue}

@@

\section{A motivating example}\label{sec:example}
%\color{black}
%\section{\textcolor{orange}{[Proof of main results]}}
\subsection{Overview}
We can use our understanding of regular singular Volterra equations study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$. In particular, we can build a frame of analytic solutions in the frequency domain by studying solutions of an integral equation in the position domain. The latter is an example of the regular singular Volterra equations we introduced above.
\subsection{Level $1$ differential equations}\label{sec:level 1 ODE}
Let $\mathcal{P}$ be a linear differential operator of the form\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}.}
%%\begin{equation}\label{eqn:level 1 ode}
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
%%\end{equation}
where
\begin{enumerate}
\item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every critical point of $P$;
\item[$\bullet$] $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R_r(z^{-1}) = \sum_{j=0}^\infty R_{r,j} z^{-j} \]
converge in the region $|z| > A$.
\end{enumerate}
Equations of the form $\mathcal{P}\Phi = 0$ are called {\em level~1} by Ecalle~\cite[Section 2.1]{EcalleIII}. In \cite{borel_reg}, we'll study different examples using Laplace transform method and our existence and uniqueness result Theorem \ref{thm:general_volterra}. 
\subsection{\textcolor{orange}{Notation}}
Previously, we studied Volterra operators with a regular singularity at $\zeta=0$. However, when we study solutions of a level 1 differential equation $\mathcal{P}\Phi=0$, we'll get many Volterra-type operators $\hat{\mathcal{P}}_\alpha$---one at each root of $\zeta=\alpha$ of the polynomial $P(-\zeta)$---with a regular singularity at $\zeta=\alpha$. Therefore, we have to set the notation, to deal with this more general situation.

Here, we'll adapt the notation of Sections \ref{sec:intro}--\ref{sec:proof_main_results} to be able to deal with singularities different from the origin. In fact, the role of the coordinate $\zeta$ will be played by $\zeta-\alpha$.

>>>>

% list formatting
\newlist{conditions}{itemize}{1}
\setlist[conditions]{leftmargin=28mm, rightmargin=12mm}
\makeatletter
% hat tip TeX.SE user31729
%   https://tex.stackexchange.com/a/328393/6934
\newcommand{\cond}[1]{\item[(\textsc{#1})]\protected@edef\@currentlabel{\textsc{#1}}}
\newcommand{\condconst}[2]{\item[($\text{\textsc{#1}} \mid #2$)]\protected@edef\@currentlabel{$\text{\textsc{#1}} \mid #2$}}
\makeatother

@@

\item \textcolor{gray}{Show that example satisfies Condition~\eqref{cond:sing}.}

@@

  \item Add a condition to ensure that $\zeta(a) = 0$ is the only singularity.
  \item \textcolor{gray}{Add $c_\Delta$ to Condition~\eqref{cond:diag-basic} as multiplicative constant, and export both of the constants $\lambda_\Delta$ and $\lambda_0 = \lambda_\Delta + c_\Delta$ from the condition.}
  \item \textcolor{gray}{When showing that the example satisfies Condition~\eqref{cond:diag-basic}, make it consistent with new condition wording.} \textcolor{MediumSpringGreen}{[No change required]}

@@

Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain. In Section~\ref{sec:example}, we'll see this helpful behavior in a certain subclass of what Ecalle calls {\em level~1} differential equations, which includes classical examples like the modified Bessel equation, the equations describing the vibration modes of beams that taper in certain ways \textcolor{orange}{[find citation]}, and the Airy equation after a change of coordinate. \textcolor{SpringGreen}{This last example generalizes to some level 1 equations that feature in current research, like the Airy-Lucas and higher Airy equations~\cite[Equations 3.2 and 3.8]{charbonnier22}\cite{durugo_higher}.}

@@

Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}. We'll achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}. We'll apply our results to level $1$ differential equations in Section~\ref{sec:example}.
\subsection{Notation for uniform bounds}
Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we'll write $\varphi \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$. Unless we say otherwise, the bound holds throughout the domain where both functions are defined.
\subsection{Setting}\label{setting}
\subsubsection{The domain}\label{setting:domain}
Throughout this paper, as described in Section~\ref{motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$. Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$. We also assume:
\begin{conditions}
\cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$. In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$. Since $\domain$ doesn't contain $\zeta = 0$, we'll always omit that starting point from the path.
\end{conditions}
For the applications we have in mind, $\domain$ might look something like the set pictured below, which satisfies Condition~\eqref{cond:star}.
\begin{center}
\begin{tikzpicture}
\newcommand{\spill}{4}
%% previously violet!20
\fill[ietcoast!33, bezier bounding box, path fading=radial edge]
  (-\spill, -\spill) (\spill, \spill)
  (0, 0) -- (160:\spill)
  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
  arc (-60:-130:\spill) -- (0, 0);
%% previously violet
\fill[ietcoast!33!black] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
\end{tikzpicture}
\end{center}
\subsubsection{The prototype operator}\label{setting:basic}
The prototypical example of the kind of operator we'll be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.

Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
\[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:
\begin{conditions}
\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---which we'll require, for simplicity, to be real and positive---the difference
\[ \hardker(a, a) - \frac{\tau}{\zeta(a)} \]
is bounded on a neighborhood of $\zeta(a) = 0$ in $\domain$.

In addition, for each $\sigma > \tau$, the bound
\[ \big|\hardker(a, a')\big| < \frac{\sigma}{\zeta(a)} \]
holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
\end{conditions}
%%Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
%%\begin{verify}
%%[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded. By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition. Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
%%\end{verify}
%%For some of our results, we'll also need to control $|p|$ and $|q|$ in various ways as $|\zeta|$ goes to infinity.
%%\begin{conditions}
%%\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
%%\begin{align*}
%%\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
%%\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
%%\end{align*}
%%outside some neighborhood of $\zeta = 0$ in $\domain$. In addition, $|1/p|$ and $|q/p|$ are bounded outside every neighborhood of $\zeta = 0$ in $\domain$; the bound may depend on the neighborhood. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point. The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
%%\end{conditions}
%%This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}. As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
For most of our results, we'll also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$. We'll require $\hardker$ to be bounded on the diagonal in $\domain^2$, and to grow at most exponentially as we move away from the diagonal. Conveniently, these two requirements can be combined into one condition. \textcolor{Tomato}{[Add only-singularity condition.]}
\begin{conditions}
\condconst{diag$_0$}{\lambda_\Delta, \lambda_0}\label{cond:diag-basic} We can find constants $\lambda_\Delta$ and $c_\Delta$ with
\[ \big| \hardker(a, a') \big| \le c_\Delta e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
for all $a$ in $\domain$ outside some neighborhood of $\zeta = 0$, and all $a' \in \domain$. In most cases, $c_\Delta$ will only enter our reasoning through the sum $\lambda_0 = \lambda_\Delta + c_\Delta$.
%%outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
\end{conditions}
We'll occasionally mention an optional condition on $p$ that allows us to state our main results more explicitly.
\begin{conditions}
\condconst{reg-p}{B, \epsilon}\label{cond:reg-p}
For some non-zero constant $B$ and some $\epsilon > 0$,
\[ p \in B\zeta + O\big(|\zeta|^{1 + \epsilon}\big) \]
at $\zeta = 0$.
\end{conditions}
\subsubsection{The perturbed operator}\label{setting:perturbed}

Now, let's perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$. The perturbation $\softpart$ doesn't have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we'll show in Proposition \ref{prop:smoothing}). To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$. This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.

@@

Now, using Condition~\eqref{cond:sing} again, choose some $\sigma > \tau$ and find a radius $r < \delta$ for which
\[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we can deduce that
\begin{align*}
|\solproto| & \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p}\right|\,|\zeta|^\tau \\
& \lesssim \left|\frac{1}{q(b')}\right|\,\frac{\sigma}{|\zeta|}\,|\zeta|^\tau \\
& \lesssim |\zeta|^{\tau-1}
\end{align*}
on the region $|\zeta| < r$, as desired.
\end{proof}
\begin{prop}\label{prop:asymptotic at infinity}
Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \textcolor{brown}{\eqref{cond:diag-basic}}. Then $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
\end{prop}
\begin{proof}
We want to show that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$.

@@

By removing a bounded neighborhood of $\zeta = 0$ from $\domain$, make a set $\domain_\text{far}$ with
\[ \hardker(a, a') \le c_\Delta e^{\lambda_\Delta |\zeta(a) - \zeta(a')|}, \]
for all $a \in \domain_\text{far}$ and $a' \in \domain$, as Condition~\eqref{cond:diag-basic} says we can do. Applying this bound on the diagonal in $\domain_\text{far}^2$, we learn that $|q/p| \le c_\Delta$ on $\domain_\text{far}$. In addition, by fixing some arbitrary  $b' \in \domain$, see that
\begin{align*}
\left|\frac{q(b')}{p(a)}\right| & \lesssim e^{\lambda_\Delta|\zeta(a) - \zeta(b')|} \\
& \lesssim e^{\lambda_\Delta(|\zeta(a)| + |\zeta(b')|)} \\
& \lesssim e^{\lambda_\Delta|\zeta(a)|} e^{\lambda_\Delta|\zeta(b')|} \\
& \lesssim e^{\lambda_\Delta|\zeta(a)|}
\end{align*}
over all $a \in \domain_\text{far}$. Hence, $|1/p| \lesssim e^{\lambda_\Delta|\zeta|}$ on $\domain_\text{far}$. Using both of the bounds we just found, we reason that
\begin{align*}
|\solproto(a)| & = \left| \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \right| \\
& \le \left|\frac{1}{p(a)}\right| \exp\left(\int_{b}^{a}\left|\frac{q}{p}\right|\;d\zeta\right) \\
& \lesssim e^{\lambda_\Delta|\zeta(a)|}\,e^{c_\Delta(|\zeta(a)| + |\zeta(b)|)} \\
& \lesssim e^{(\lambda_\Delta + c_\Delta)|\zeta(a)|}\,e^{c_\Delta|\zeta(b)|} \\
& \lesssim e^{\lambda_0|\zeta(a)|}
\end{align*}
over all $a \in \domain_\text{far}$, recalling that $\lambda_0 = \lambda_\Delta + c_\Delta$. Since $\domain_\text{far}$ avoids a neighborhood of $\zeta = 0$, we know $|\zeta|^{\tau-1}$ is bounded on $\domain_\text{far}$. Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{far}$.

Finally, let $\domain_\text{mid}$ be the set that remains when you remove $\domain_\text{near}$ and $\domain_\text{far}$ from $\domain$. Since $\domain_\text{mid}$ avoids $\zeta = 0$ and is bounded, $|\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ can't get arbitrarily small there, and \textcolor{MediumSpringGreen}{Condition~[add a new condition for this]} guarantees that $|\solproto|$ is bounded there. Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{mid}$.

@@

First, choose some $\sigma_0 \in (\tau, \sigma)$. Condition~\eqref{cond:sing} tells us that by making $\delta > 0$ small enough, we can ensure that
\[ |\hardker(a, a')| \le \frac{\sigma_0}{|\zeta(a)|} \]
whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
\par\color{RoyalBlue}

@@

\section{A motivating example}\label{sec:example}
%\color{black}
%\section{\textcolor{orange}{[Proof of main results]}}
\subsection{Overview}
We can use our understanding of regular singular Volterra equations study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$. In particular, we can build a frame of analytic solutions in the frequency domain by studying solutions of an integral equation in the position domain. The latter is an example of the regular singular Volterra equations we introduced above.
\subsection{Level $1$ differential equations}\label{sec:level 1 ODE}
Let $\mathcal{P}$ be a linear differential operator of the form\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}.}
%%\begin{equation}\label{eqn:level 1 ode}
\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
%%\end{equation}
where
\begin{enumerate}
\item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every critical point of $P$;
\item[$\bullet$] $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
\[ R_r(z^{-1}) = \sum_{j=0}^\infty R_{r,j} z^{-j} \]
converge in the region $|z| > A$.
\end{enumerate}
Equations of the form $\mathcal{P}\Phi = 0$ are called {\em level~1} by Ecalle~\cite[Section 2.1]{EcalleIII}. In \cite{borel_reg}, we'll study different examples using Laplace transform method and our existence and uniqueness result Theorem \ref{thm:general_volterra}. 
\subsection{Notation}\label{sec:notation_alpha}
Previously, we studied Volterra operators with a regular singularity at $\zeta=0$. However, when we look at solutions of a level 1 differential equation $\mathcal{P}\Phi=0$, we'll get many Volterra-type operators $\hat{\mathcal{P}}_\alpha$---one at each root of $\zeta=\alpha$ of the polynomial $P(-\zeta)$---with a regular singularity at $\zeta=\alpha$.

Here, we adapt the notation of Sections \ref{sec:intro}--\ref{sec:proof_main_results}, to deal with this more general situation. First of all, the role of the coordinate $\zeta$ will be played by $\zeta-\alpha$. As a consequence, references to the point $\zeta=0$ become references to the point $\zeta-\alpha=0$, or equivalently $\zeta=\alpha$.

Recalling that $\domain$ is star-shaped around $\zeta=0$ (see Condition \eqref{cond:star}), we introduce the notation $\domain_\alpha$ for domains star-shaped around $\zeta=\alpha$. Then, the function space $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ is the space of holomorphic functions in $\domain_\alpha$, uniformly of exponential type $\Lambda$ and with a power-law singularity at $\zeta=\alpha$. Explicitly, $f\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ if

\[ e^{-\Lambda |\zeta-\alpha|} |\zeta-\alpha|^{-\sigma} |f| \]

is uniformly bounded in $\domain_\alpha$.
